The ITKv4 registration framework

### 2016-07-17 papers/papers.Rmd
ENH:  IBM presentation.

# Major papers

@@

<BR><BR>
<span style="color:red;">_"Papers are just advertisements for the science."_</red>
<BR>

@@

<!--
NOtes:
* Previously discussed Brians work
* The variant most widely used
-->

@@

--------------------------------------------------------------------------------------
Script by Nick Tustison
--------------------------------------------------------------------------------------
Apple XGrid support by Craig Stark
--------------------------------------------------------------------------------------
```

@@

* "*Let's incorporate N3 into ANTs!*"

@@

<!-- regular html comment

@@

* tested nightly within the ITK dashboard system

@@

##  Atropos -- cutting the threads of fate

![](./papers/figures/Atropos_deGoya.jpg)

@@

![](./tools/atropos/figures/atroposFlow.png)

>>>>

# Major ANTs utilities

@@

<BR><BR>
_\`\`Papers are just advertisements for the science.\'\'_
<BR>

## Neuro tools

![](./tools/figures/coreANtsToolsNeuro.png)

## Pulmonary tools

![](./tools/figures/coreANtsToolsLung.png)

<!--

@@

NOtes:
* Previously discussed Brians work
* The variant most widely used
-->

<!--

## Diffeomorphisms:  Occam's razor modeling

![](./figures/sillyputty.png)

_differentiable map with differentiable inverse_

## Diffeomoprhisms:  differentiable map with diff. inverse

![](./figures/highresdiffeos.jpg)

<!--

## Diffeomorphisms: image parameterization in a metric space

![](./figures/shape_appearance.png)
-->

@@

--------------------------------------------------------------------------------------
script adapted by N.M. van Strien, http://www.mri-tutorial.com | NTNU MR-Center
multivariate template adaption by Nick Tustison
--------------------------------------------------------------------------------------
Apple XGrid support by Craig Stark
--------------------------------------------------------------------------------------
```

<!--

@@

* "*Let's incorporate N3 into ANTs!*"
-->

@@

@@

* tested nightly within the ITK dashboard system
-->

@@

<--
##  Atropos -- cutting the threads of fate

![](./papers/figures/Atropos_deGoya.jpg)
-->

@@

![](./tools/atropos/figures/atroposFlow.png)
-->

## ```DenoiseImage``` --- contribution from Jose Manjon

```bash
$ DenoiseImage --help

COMMAND:
     DenoiseImage
          Denoise an image using a spatially adaptive filter originally described in J. V.
          Manjon, P. Coupe, Luis Marti-Bonmati, D. L. Collins, and M. Robles. Adaptive
          Non-Local Means Denoising of MR Images With Spatially Varying Noise Levels,
          Journal of Magnetic Resonance Imaging, 31:192-203, June 2010.

OPTIONS:
     -d, --image-dimensionality 2/3/4
          This option forces the image to be treated as a specified-dimensional image. If
          not specified, the program tries to infer the dimensionality from the input
          image.

     -i, --input-image inputImageFilename
          A scalar image is expected as input for noise correction.

     -n, --noise-model Rician/(Gaussian)
          Employ a Rician or Gaussian noise model.

     -x, --mask-image maskImageFilename
          If a mask image is specified, denoising is only performed in the mask region.

     -s, --shrink-factor (1)/2/3/...
          Running noise correction on large images can be time consuming. To lessen
          computation time, the input image can be resampled. The shrink factor, specified
          as a single integer, describes this resampling. Shrink factor = 1 is the
          default.

     -p, --patch-radius 1
                        1x1x1
          Patch radius. Default = 1x1x1

     -r, --search-radius 3
                         3x3x3
          Search radius. Default = 3x3x3.

     -o, --output correctedImage
                  [correctedImage,<noiseImage>]
          The output consists of the noise corrected version of the input image.
          Optionally, one can also output the estimated noise image.

     --help
          Print the help menu.
          <VALUES>: 1

```

## Multi-atlas segmentation

![](./tools/jointfusion/figures/jointLabelFusion.png)

## New work:  joint intensity fusion

![](./tools/jointfusion/figures/jointIntensityFusion.png)

## Possible uses

* ``Correct'' images

    * motion correction

    * ``remove'' lesions

* Project atlas set intensity signature

* Use in ``corrective learning''

## ```antsJointFusion``` --- contribution from Hongzhi Wang (with some added features)

```bash
$ antsJointFusion --help

COMMAND:
     antsJointFusion
          antsJointFusion is an image fusion algorithm developed by Hongzhi Wang and Paul
          Yushkevich which won segmentation challenges at MICCAI 2012 and MICCAI 2013. The
          original label fusion framework was extended to accommodate intensities by Brian
          Avants. This implementation is based on Paul's original ITK-style implementation
          and Brian's ANTsR implementation. References include 1) H. Wang, J. W. Suh, S.
          Das, J. Pluta, C. Craige, P. Yushkevich, Multi-atlas segmentation with joint
          label fusion IEEE Trans. on Pattern Analysis and Machine Intelligence, 35(3),
          611-623, 2013. and 2) H. Wang and P. A. Yushkevich, Multi-atlas segmentation
          with joint label fusion and corrective learning--an open source implementation,
          Front. Neuroinform., 2013.

OPTIONS:
     -d, --image-dimensionality 2/3/4
          This option forces the image to be treated as a specified-dimensional image. If
          not specified, the program tries to infer the dimensionality from the input
          image.

     -t, --target-image targetImage
                        [targetImageModality0,targetImageModality1,...,targetImageModalityN]
          The target image (or multimodal target images) assumed to be aligned to a common
          image domain.

     -g, --atlas-image atlasImage
                       [atlasImageModality0,atlasImageModality1,...,atlasImageModalityN]
          The atlas image (or multimodal atlas images) assumed to be aligned to a common
          image domain.

     -l, --atlas-segmentation atlasSegmentation
          The atlas segmentation images. For performing label fusion the number of
          specified segmentations should be identical to the number of atlas image sets.

     -a, --alpha 0.1
          Regularization term added to matrix Mx for calculating the inverse. Default =
          0.1

     -b, --beta 2.0
          Exponent for mapping intensity difference to the joint error. Default = 2.0

     -r, --retain-label-posterior-images (0)/1
          Retain label posterior probability images. Requires atlas segmentations to be
          specified. Default = false

     -f, --retain-atlas-voting-images (0)/1
          Retain atlas voting images. Default = false

     -c, --constrain-nonnegative (0)/1
          Constrain solution to non-negative weights.

     -p, --patch-radius 2
                        2x2x2
          Patch radius for similarity measures. Default = 2x2x2

     -m, --patch-metric (PC)/MSQ
          Metric to be used in determining the most similar neighborhood patch. Options
          include Pearson's correlation (PC) and mean squares (MSQ). Default = PC (Pearson
          correlation).

     -s, --search-radius 3
                         3x3x3
                         searchRadiusMap.nii.gz
          Search radius for similarity measures. Default = 3x3x3. One can also specify an
          image where the value at the voxel specifies the isotropic search radius at that
          voxel.

     -e, --exclusion-image label[exclusionImage]
          Specify an exclusion region for the given label.

     -x, --mask-image maskImageFilename
          If a mask image is specified, fusion is only performed in the mask region.

     -o, --output labelFusionImage
                  intensityFusionImageFileNameFormat
                  [labelFusionImage,intensityFusionImageFileNameFormat,<labelPosteriorProbabilityImageFileNameFormat>,<atlasVotingWeightImageFileNameFormat>]
          The output is the intensity and/or label fusion image. Additional optional
          outputs include the label posterior probability images and the atlas voting
          weight images.

     --version
          Get version information.

     --help
          Print the help menu.
          <VALUES>: 1

```
